Hybrid compiler-library approach to efficiently compile Numpy expressions

### 2013-04-06 doc/papers/cpc2013/paper.tex
Take into account Pierrick's advice.

    The Numpy module for the Python language is growing in popularity among the
    scientific community as a scientific computing tool. It most noticeably
    provides a N-dimensional array object and a set of mathematical arrays
    using this structure that provide efficient computations thanks to the use
    of natively compiled implementation.

>>>>

    The Numpy module for the Python language is growing in popularity among the
    scientific community as a scientific computing tool. It most noticeably
    provides a N-dimensional array object and a set of mathematical operators
    using this structure that provide efficient computations thanks to the use
    of natively compiled implementation.
